---
title: "coursera_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{coursera_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
install.packages('devtools')
library(devtools)
install_github('mmansolf/CourseraPkg')
library(CourseraPkg)
# load_all()
```

# Overview

This package provides functions for reading, summarizing, and plotting accident data files with a structure specific to this package. This vignette and package were created as part of the Coursera course "Building R Packages".

# Functions

This package contains the following functions:

* fars_read: Read an accident file
* make_filename: Makes a filename for use in fars_read
* fars_read_years: Reads dataset(s) for provided year(s)
* fars_summarize_years: Count accidents by provided year(s)
* fars_map_state: Plot accidents for provided year

# The final products

For illustration purposes in this vignette, I will only demonstrate the two functions fars_summarize_years and fars_map_state which produce interpretable output, rather than simply character strings or data sets.

## fars_map_state

This function reads a list of files specified by a set of year values, counts the number of records in each year-month combination, and pivots to wide format with separate columns per year.

```{r}
fars_summarize_years(c(2013,2014))
```

## fars_summarize_years

This function reads a file specified by a year value and plots accidents in the state.

```{r}
fars_map_state(05,2013)
```
